CommonMind Consortium: DLPFC

### 2020-09-19 combined_analysis/diff.networks.Rmd
Update diff networks

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf combined_analysis/diff.networks_cache
ml git pandoc udunits proj gdal geos
git pull
R

@@

minClusterSize = 50
```

@@

@@

>>>>

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf combined_analysis/diff.networks_* combined_analysis/diff.networks.html
ml git pandoc udunits proj gdal geos
git pull
R

@@

minClusterSize = 20
```

@@

rstat_nodes <- data.frame(name = c("Hadley", "David", "Romain", "Julia"))
rstat_edges <- data.frame(from = c(1, 1, 1, 2, 3, 3, 4, 4, 4),
                         to = c(2, 3, 4, 1, 1, 2, 1, 2, 3))
rstat_edges$weight = rnorm(9)

@@

ggraph(net, layout = "stress") + 
  geom_node_point(size=10, color="blue") +
  geom_edge_link(aes(width = weight), alpha = 0.8) + 
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_text(aes(label = name), repel = TRUE) +
  labs(edge_width = "Correlation") +
  theme_graph()
